\begin{minipage}{\textwidth} \centering Analyzing rasters, vectors and time series using new Python interfaces in GRASS GIS 7 \bigskip \end{minipage}

### 2015-03-25 grassposter/2015_EGU_G7_Python/main.tex
Added Thuenen Institute Logo
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64911 15284696-431f-4ddb-bdfa-cd5b030d7da7
Added GRASS GIS Temporal Framework part
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64917 15284696-431f-4ddb-bdfa-cd5b030d7da7

       \logovspace
       % TODO: TICSA logo (Soeren)
       \includegraphics[width=\logowidth]{ncstate}
       \logohspace
       \includegraphics[width=\logowidth]{ctu_prague}
       \logohspace
       \includegraphics[width=\logowidth]{eurac}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Temporal framework}}{
\cite{Gebbert2014}
}

>>>>

       \logovspace
       % TODO: TICSA logo (Soeren)
       \includegraphics[width=\logowidth]{ti}
       \logohspace
       \includegraphics[width=\logowidth]{ctu_prague}
       \logohspace
       \includegraphics[width=\logowidth]{eurac}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{GRASS GIS Temporal Framework}}{
The GRASS GIS Temporal Framework implements the temporal GIS functionality of GRASS GIS 
and provides a Python API to implement spatio-temporal processing modules. 
The framework introduces space time datasets that represent time series of raster, 
3D raster or vector maps. Some API examples:
\includegraphics[width=1\linewidth, clip, trim=0 0 0 0]{tgrass_examples}
}
